---
# title: 
output: 
  word_document:
    reference_docx: PIFSC_style_simple.docx
# date: 
---

``` {r read_in_data, include = FALSE, eval = TRUE}
# knitr::opts_chunk$set(cache = TRUE)
# knitr::opts_chunk$set(eval = FALSE)

if (!require("pacman")) install.packages("pacman")
    pacman::p_load(reshape, dplyr, ggplot2, magrittr, assertthat, gridExtra, readxl, this.path, kableExtra, flextable, gt, officer, grid)

# turn off scientific notation in console output
  options(scipen=999)

  this_dir <- this.path::here(.. = 0)
  
# load the workspace containing our simulated populations from create_simulated_pops.R
  load(paste0(this_dir, "/simulated_pops.RData"))

# load in the workspace containing our growth parm estimates based on the original (pre Sette-2025-04 cruise) sample distributions
#   this workspace was made in create_simulated_pops.R and only needs to be updated if we change the values in
# BMUS_LH_sim_pop_parmaters.xls or if the list of "unfished CNMI" samples that Eva originally gave me gets changed.
  load(paste0(this_dir, "/original_sample_fits_2July.RData"))

# read in the modified LH Sampling functions
  source(paste0(this_dir, "/modify_LH_sample_function.R"))
  
# load the plotting functions we will use
  source(paste0(this_dir, "/plotting_functions.R")) 
  
# read in the .csv file with the species and lengths that we have
 have_lengths <- read.csv(paste0(this_dir,"\\cnmi_unfished_samples_update.csv"),header=T)
#  have_lengths <- read.csv(paste0(this_dir,"\\cnmi_unfished_samples.csv"),header=T)
  have_lengths <- have_lengths[,c(2,5,10)]
  
  names(have_lengths)[] <- c('species','length','type')
```

``` {r read_in_new_lengths, include = FALSE, eval = TRUE}
# new_lengths <- as.data.frame(read_excel(paste0(this_dir, "/SE-25-04_data_07152025_Alamagan.xlsx")))
new_lengths <- as.data.frame(read_excel(paste0(this_dir, "/SE-25-04_data_07202025.xlsx")))

```


``` {r , include = FALSE, eval = TRUE}
# define leading values for this species
  short_name <- 'APRU'
  full_name <- 'Aphareus rutilans'
  sim_output <- sim_pop_harv_output <- APRU
  bin_width <- 5
  sim_fit_original <- APRU_sim_fit_org
    
# filter new lengths    
  have <- subset(have_lengths, species ==  full_name)
  have_new <- subset(new_lengths, SPECIES_CODE == short_name)
  
  
  build_new <- data.frame('species' = full_name, 'length' = as.numeric(have_new$FL_cm), 'type' = 'new')
  have <- rbind(have, build_new)
  
# return the plan for the updated samples  
  sample_plan <- plan_updated <- get_plan(have, bin_width, original=FALSE)

# bootstrap samples and fit von B parms
  n_boots <- 100
  age_max <- sim_output$parameters$age_max
  save_bootstraps <- FALSE

  sim_fit_update <- fit_plan(sample_plan, sim_output, n_boots, age_max, save_bootstraps)
  
```


## *`r full_name`* / `r short_name` / Lehi

```{r fig.cap = "", echo=FALSE,eval=TRUE,messages=FALSE,warning=FALSE, fig.height = 3, fig.width = 6.5}
plot_LH_have(have, bin_width)
```

```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 6.5}
parm_plots <- parm_abs_error_plot(sim_fit_original, sim_fit_update)
grid.arrange(grobs=parm_plots, ncol=3)
```

Figure. Samples of `r short_name` by length and simulated estimates of von Bertalanffy growth parameters based on samples available before Sette-2025-04 (blue) and updated to include fish lengths observed during the cruise (pink). The true population value for each parameter is shown as a broken black line.



``` {r , include = FALSE, eval = TRUE}
# define leading values for this species
  short_name <- 'CALU'
  full_name <- 'Caranx lugubris'
  bin_width <- 5
    
# filter lengths    
  have <- subset(have_lengths, species ==  full_name)
  have_new <- subset(new_lengths, SPECIES_CODE == short_name)
  build_new <- data.frame('species' = full_name, 'length' = as.numeric(have_new$FL_cm), 'type' = 'new')
  have <- rbind(have, build_new)
  
  
```

\newpage
## *`r full_name`* / `r short_name` / Black Jack

```{r fig.cap = "", echo=FALSE,eval=TRUE,messages=FALSE,warning=FALSE, fig.height = 3, fig.width = 6.5}
plot_LH_have(have, bin_width)
```



``` {r , include = FALSE, eval = TRUE}
# define leading values for this species
  short_name <- 'ETCA'
  full_name <- 'Etelis carbunculus'
  sim_output <- sim_pop_harv_output <- ETCA
  bin_width <- 5
  sim_fit_original <- ETCA_sim_fit_org
    
# filter new lengths   
  have <- subset(have_lengths, species ==  full_name)
   have_new <- subset(new_lengths, SPECIES_CODE == short_name)
  build_new <- data.frame('species' = full_name, 'length' = as.numeric(have_new$FL_cm), 'type' = 'new')
  have <- rbind(have, build_new)
  
# what is rel POS?
POS_N <- 500
POS_plan <-  find_POS(sim_output, POS_N, bin_width)
POS_plan$rel_plan <- POS_plan$plan/POS_N

# return the plan for the updated samples  
  sample_plan <- plan_updated <- get_plan(have, bin_width, original=FALSE)

# modify sample_plan to better match POS
new_plan <- cbind(sample_plan, POS_plan$rel_plan)  
names(new_plan)[3] <- 'pos_rel'
new_plan$pos_abs <- round(sum(new_plan$nsamps)*new_plan$pos_rel,0)
new_plan$new_nsamps <- new_plan$nsamps

for (i in 1:nrow(new_plan)) {
    if(new_plan$pos_abs[i] < new_plan$nsamps[i]) {
      new_plan$new_nsamps[i] <- new_plan$pos_abs[i]
    }
}

sample_plan <- new_plan[,c(1,5)]
names(sample_plan)[2] <- 'nsamps'

# bootstrap samples and fit von B parms
  n_boots <- 100
  age_max <- sim_output$parameters$age_max
  save_bootstraps <- FALSE

  sim_fit_update <- fit_plan(sample_plan, sim_output, n_boots, age_max, save_bootstraps)
  
```

\newpage
## *`r full_name`* / `r short_name` / Ehu

```{r fig.cap = "", echo=FALSE,eval=TRUE,messages=FALSE,warning=FALSE, fig.height = 3, fig.width = 6.5}
plot_LH_have(have, bin_width)
```

```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 6.5}
parm_plots <- parm_abs_error_plot(sim_fit_original, sim_fit_update)
grid.arrange(grobs=parm_plots, ncol=3)
```

Figure. Samples of `r short_name` by length and simulated estimates of von Bertalanffy growth parameters based on samples available before Sette-2025-04 (blue) and updated to include fish lengths observed during the cruise (pink). The true population value for each parameter is shown as a broken black line.





``` {r , include = FALSE, eval = TRUE}
# define leading values for this species
  short_name <- 'ETCO'
  full_name <- 'Etelis coruscans'
  sim_output <- sim_pop_harv_output <- ETCO
  bin_width <- 5
  sim_fit_original <- ETCO_sim_fit_org
    
# filter lengths    
  have <- subset(have_lengths, species ==  full_name)
   have_new <- subset(new_lengths, SPECIES_CODE == short_name)
  build_new <- data.frame('species' = full_name, 'length' = as.numeric(have_new$FL_cm), 'type' = 'new')
  have <- rbind(have, build_new)
  
# return the plan for the updated samples  
  sample_plan <- plan_updated <- get_plan(have, bin_width, original=FALSE)

# bootstrap samples and fit von B parms
  n_boots <- 100
  age_max <- sim_output$parameters$age_max
  save_bootstraps <- FALSE

  sim_fit_update <- fit_plan(sample_plan, sim_output, n_boots, age_max, save_bootstraps)
  
```

\newpage
## *`r full_name`* / `r short_name` / Onaga

```{r fig.cap = "", echo=FALSE,eval=TRUE,messages=FALSE,warning=FALSE, fig.height = 3, fig.width = 6.5}
plot_LH_have(have, bin_width)
```

```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 6.5}
parm_plots <- parm_abs_error_plot(sim_fit_original, sim_fit_update)
grid.arrange(grobs=parm_plots, ncol=3)
```

Figure. Samples of `r short_name` by length and simulated estimates of von Bertalanffy growth parameters based on samples available before Sette-2025-04 (blue) and updated to include fish lengths observed during the cruise (pink). The true population value for each parameter is shown as a broken black line.



``` {r , include = FALSE, eval = TRUE}
# define leading values for this species
  short_name <- 'PRAU'
  full_name <- 'Pristipomoides auricilla'
  sim_output <- sim_pop_harv_output <- PRAU
  bin_width <- 2
  sim_fit_original <- PRAU_sim_fit_org
    
# filter lengths    
  have <- subset(have_lengths, species ==  full_name)
   have_new <- subset(new_lengths, SPECIES_CODE == short_name)
  build_new <- data.frame('species' = full_name, 'length' = as.numeric(have_new$FL_cm), 'type' = 'new')
  have <- rbind(have, build_new)
  
# return the plan for the updated samples  
  sample_plan <- plan_updated <- get_plan(have, bin_width, original=FALSE)

# bootstrap samples and fit von B parms
  n_boots <- 100
  age_max <- sim_output$parameters$age_max
  save_bootstraps <- FALSE

  sim_fit_update <- fit_plan(sample_plan, sim_output, n_boots, age_max, save_bootstraps)
  
```

\newpage
## *`r full_name`* / `r short_name` / Kalekale

```{r fig.cap = "", echo=FALSE,eval=TRUE,messages=FALSE,warning=FALSE, fig.height = 3, fig.width = 6.5}
plot_LH_have(have, bin_width)
```

```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 6.5}
parm_plots <- parm_abs_error_plot(sim_fit_original, sim_fit_update)
grid.arrange(grobs=parm_plots, ncol=3)
```

Figure. Samples of `r short_name` by length and simulated estimates of von Bertalanffy growth parameters based on samples available before Sette-2025-04 (blue) and updated to include fish lengths observed during the cruise (pink). The true population value for each parameter is shown as a broken black line.



``` {r , include = FALSE, eval = TRUE}
# define leading values for this species
  short_name <- 'PRFI'
  full_name <- 'Pristipomoides filamentosus'
  sim_output <- sim_pop_harv_output <- PRFI
  bin_width <- 2
  sim_fit_original <- PRFI_sim_fit_org
    
# filter lengths    
  have <- subset(have_lengths, species ==  full_name)
   have_new <- subset(new_lengths, SPECIES_CODE == short_name)
  build_new <- data.frame('species' = full_name, 'length' = as.numeric(have_new$FL_cm), 'type' = 'new')
  have <- rbind(have, build_new)
  

# what is rel POS?
POS_N <- 500
POS_plan <-  find_POS(sim_output, POS_N, bin_width)
POS_plan$rel_plan <- POS_plan$plan/POS_N

# return the plan for the updated samples  
  sample_plan <- plan_updated <- get_plan(have, bin_width, original=FALSE)

# modify sample_plan to better match POS
new_plan <- cbind(sample_plan[1:nrow(POS_plan),], POS_plan$rel_plan)  
names(new_plan)[3] <- 'pos_rel'
new_plan$pos_abs <- round(sum(new_plan$nsamps)*new_plan$pos_rel,0)
new_plan$new_nsamps <- new_plan$nsamps

for (i in 1:nrow(new_plan)) {
    if(new_plan$pos_abs[i] < new_plan$nsamps[i]) {
      new_plan$new_nsamps[i] <- new_plan$pos_abs[i]
    }
}

sample_plan <- new_plan[,c(1,5)]
names(sample_plan)[2] <- 'nsamps'


# bootstrap samples and fit von B parms
  n_boots <- 100
  age_max <- sim_output$parameters$age_max
  save_bootstraps <- FALSE

  sim_fit_update <- fit_plan(sample_plan, sim_output, n_boots, age_max, save_bootstraps)
  
```

\newpage
## *`r full_name`* / `r short_name` / Opakapaka / Brown paka

```{r fig.cap = "", echo=FALSE,eval=TRUE,messages=FALSE,warning=FALSE, fig.height = 3, fig.width = 6.5}
plot_LH_have(have, bin_width)
```

```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 6.5}
parm_plots <- parm_abs_error_plot(sim_fit_original, sim_fit_update)
grid.arrange(grobs=parm_plots, ncol=3)
```

Figure. Samples of `r short_name` by length and simulated estimates of von Bertalanffy growth parameters based on samples available before Sette-2025-04 (blue) and updated to include fish lengths observed during the cruise (pink). The true population value for each parameter is shown as a broken black line.




``` {r , include = FALSE, eval = TRUE}
# define leading values for this species
  short_name <- 'PRFL'
  full_name <- 'Pristipomoides flavipinnis'
  sim_output <- sim_pop_harv_output <- PRFL
  bin_width <- 2
  sim_fit_original <- PRFL_sim_fit_org
    
# filter lengths    
  have <- subset(have_lengths, species ==  full_name)
   have_new <- subset(new_lengths, SPECIES_CODE == short_name)
  build_new <- data.frame('species' = full_name, 'length' = as.numeric(have_new$FL_cm), 'type' = 'new')
  have <- rbind(have, build_new)

  
# what is rel POS?
POS_N <- 500
POS_plan <-  find_POS(sim_output, POS_N, bin_width)
POS_plan$rel_plan <- POS_plan$plan/POS_N

# return the plan for the updated samples  
  sample_plan <- plan_updated <- get_plan(have, bin_width, original=FALSE)

# modify sample_plan to better match POS
new_plan <- cbind(sample_plan[1:nrow(POS_plan),], POS_plan$rel_plan)  
names(new_plan)[3] <- 'pos_rel'
new_plan$pos_abs <- round(sum(new_plan$nsamps)*new_plan$pos_rel,0)
new_plan$new_nsamps <- new_plan$nsamps

for (i in 1:nrow(new_plan)) {
    if(new_plan$pos_abs[i] < new_plan$nsamps[i]) {
      new_plan$new_nsamps[i] <- new_plan$pos_abs[i]
    }
}

sample_plan <- new_plan[,c(1,5)]
names(sample_plan)[2] <- 'nsamps'

# bootstrap samples and fit von B parms
  n_boots <- 100
  age_max <- sim_output$parameters$age_max
  save_bootstraps <- FALSE

  sim_fit_update <- fit_plan(sample_plan, sim_output, n_boots, age_max, save_bootstraps)
  
```

\newpage
## *`r full_name`* / `r short_name` / Yellow-eye paka

```{r fig.cap = "", echo=FALSE,eval=TRUE,messages=FALSE,warning=FALSE, fig.height = 3, fig.width = 6.5}
plot_LH_have(have, bin_width)
```

```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 6.5}
parm_plots <- parm_abs_error_plot(sim_fit_original, sim_fit_update)
grid.arrange(grobs=parm_plots, ncol=3)
```

Figure. Samples of `r short_name` by length and simulated estimates of von Bertalanffy growth parameters based on samples available before Sette-2025-04 (blue) and updated to include fish lengths observed during the cruise (pink). The true population value for each parameter is shown as a broken black line.




``` {r , include = FALSE, eval = TRUE}
# define leading values for this species
  short_name <- 'PRZO'
  full_name <- 'Pristipomoides zonatus'
  sim_output <- sim_pop_harv_output <- PRZO
  bin_width <- 2
  sim_fit_original <- PRZO_sim_fit_org
    
# filter lengths    
  have <- subset(have_lengths, species ==  full_name)
   have_new <- subset(new_lengths, SPECIES_CODE == short_name)
  build_new <- data.frame('species' = full_name, 'length' = as.numeric(have_new$FL_cm), 'type' = 'new')
  have <- rbind(have, build_new)
  
# return the plan for the updated samples  
  sample_plan <- plan_updated <- get_plan(have, bin_width, original=FALSE)

# bootstrap samples and fit von B parms
  n_boots <- 100
  age_max <- sim_output$parameters$age_max
  save_bootstraps <- FALSE

  sim_fit_update <- fit_plan(sample_plan, sim_output, n_boots, age_max, save_bootstraps)
```

\newpage
## *`r full_name`* / `r short_name` / Gindai


```{r fig.cap = "", echo=FALSE,eval=TRUE,messages=FALSE,warning=FALSE, fig.height = 3, fig.width = 6.5}
plot_LH_have(have, bin_width)
```

```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 6.5}
parm_plots <- parm_abs_error_plot(sim_fit_original, sim_fit_update)
grid.arrange(grobs=parm_plots, ncol=3)
```

Figure. Samples of `r short_name` by length and simulated estimates of von Bertalanffy growth parameters based on samples available before Sette-2025-04 (blue) and updated to include fish lengths observed during the cruise (pink). The true population value for each parameter is shown as a broken black line.


