---
# title: 
output: 
  word_document:
    reference_docx: PIFSC_style_simple.docx
# date: 
---

``` {r read_in_data, include = FALSE, eval = TRUE}
# knitr::opts_chunk$set(cache = TRUE)
# knitr::opts_chunk$set(eval = FALSE)

if (!require("pacman")) install.packages("pacman")
    pacman::p_load(reshape, dplyr, ggplot2, magrittr, assertthat, gridExtra, readxl, this.path, kableExtra, flextable, gt, officer)

# turn off scientific notation in console output
  options(scipen=999)

  this_dir <- this.path::here(.. = 0)
  
# load the workspace containing our simulated populations
  load(paste0(this_dir, "/simulated_pops.RData"))

# read in the modified LH Sampling functions
  source(paste0(this_dir, "/modify_LH_sample_function.R"))
  
# load the plotting functions we will use
  source(paste0(this_dir, "/plotting_functions.R")) 
  
# read in the .csv file with the species and lengths that we have
  have_lengths <- read.csv(paste0(this_dir,"\\cnmi_unfished_samples.csv"),header=T)
  have_lengths <- have_lengths[,c(2,5,10)]
  
  names(have_lengths)[] <- c('species','length','type')
```

``` {r , include = FALSE, eval = TRUE}
  short_name <- 'PRZO'
  full_name <- 'Pristipomoides zonatus'
  sim_pop_harv_output <- PRZO
    
  have <- subset(have_lengths, species ==  full_name)
  hist_have <- hist(have$length, breaks = seq(0,120,5),include.lowest=TRUE, right=FALSE,plot=TRUE)

  we_have <- data.frame('binL' = hist_have$breaks[1:(length(hist_have$breaks)-1)], 'have' = hist_have$counts)

  
```

## *`r full_name`* / `r short_name`


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 6.5, fig.width = 6.5}
plot_pop_vb_parms(sim_pop_harv_output)
```

Figure. Simulated population von Bertalanffy growth parameters for `r short_name`. Natural mortality is dependent on length via Lorenzen, overall **M = `r this_M`**. Max age is **`r this_Amax` years**. Vertical line is the population median for each parameter. The value of the correlation coefficient is printed on the lower right plot where the theoretical relationship between Linf and k is denoted by the broken red line.


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 5}
plot_pop_n_at_age(sim_pop_harv_output)
```

Figure. Simulated `r short_name` unfished population length composition.

|
|


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 4, fig.width = 5}
plot_fit_pop(sim_pop_harv_output)
```

Figure. Simulated `r short_name` unfished population with the fitted von Bertalanffy growth function.




``` {r ETCA, include = FALSE, eval = TRUE}

  short_name <- 'ETCA'
  full_name <- 'E. carbunculus'
  sim_pop_harv_output <- ETCA
  this_M <- sim_pop_harv_output$parameters$M
  this_Amax <- sim_pop_harv_output$parameters$Amax
    
```

## *`r full_name`* / `r short_name`


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 6.5, fig.width = 6.5}
plot_pop_vb_parms(sim_pop_harv_output)
```

Figure. Simulated population von Bertalanffy growth parameters for `r short_name`. Natural mortality is dependent on length via Lorenzen, overall **M = `r this_M`**. Max age is **`r this_Amax` years**. Vertical line is the population median for each parameter. The value of the correlation coefficient is printed on the lower right plot where the theoretical relationship between Linf and k is denoted by the broken red line.


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 5}
plot_pop_n_at_age(sim_pop_harv_output)
```

Figure. Simulated `r short_name` unfished population length composition.

|
|


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 4, fig.width = 5}
plot_fit_pop(sim_pop_harv_output)
```

Figure. Simulated `r short_name` unfished population with the fitted von Bertalanffy growth function.






``` {r ETCO, include = FALSE, eval = TRUE}

  short_name <- 'ETCO'
  full_name <- 'E. coruscans'
  sim_pop_harv_output <- ETCO
  this_M <- sim_pop_harv_output$parameters$M
  this_Amax <- sim_pop_harv_output$parameters$Amax
    
```

## *`r full_name`* / `r short_name`


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 6.5, fig.width = 6.5}
plot_pop_vb_parms(sim_pop_harv_output)
```

Figure. Simulated population von Bertalanffy growth parameters for `r short_name`. Natural mortality is dependent on length via Lorenzen, overall **M = `r this_M`**. Max age is **`r this_Amax` years**. Vertical line is the population median for each parameter. The value of the correlation coefficient is printed on the lower right plot where the theoretical relationship between Linf and k is denoted by the broken red line.


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 5}
plot_pop_n_at_age(sim_pop_harv_output)
```

Figure. Simulated `r short_name` unfished population length composition.

|
|


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 4, fig.width = 5}
plot_fit_pop(sim_pop_harv_output)
```

Figure. Simulated `r short_name` unfished population with the fitted von Bertalanffy growth function.



``` {r PRAU, include = FALSE, eval = TRUE}

  short_name <- 'PRAU'
  full_name <- 'P. auricilla'
  sim_pop_harv_output <- PRAU
  this_M <- sim_pop_harv_output$parameters$M
  this_Amax <- sim_pop_harv_output$parameters$Amax
    
```

## *`r full_name`* / `r short_name`


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 6.5, fig.width = 6.5}
plot_pop_vb_parms(sim_pop_harv_output)
```

Figure. Simulated population von Bertalanffy growth parameters for `r short_name`. Natural mortality is dependent on length via Lorenzen, overall **M = `r this_M`**. Max age is **`r this_Amax` years**. Vertical line is the population median for each parameter. The value of the correlation coefficient is printed on the lower right plot where the theoretical relationship between Linf and k is denoted by the broken red line.


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 5}
plot_pop_n_at_age(sim_pop_harv_output)
```

Figure. Simulated `r short_name` unfished population length composition.

|
|


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 4, fig.width = 5}
plot_fit_pop(sim_pop_harv_output)
```

Figure. Simulated `r short_name` unfished population with the fitted von Bertalanffy growth function.



``` {r PRFI, include = FALSE, eval = TRUE}

  short_name <- 'PRFI'
  full_name <- 'P. filamentosus'
  sim_pop_harv_output <- PRFI
  this_M <- sim_pop_harv_output$parameters$M
  this_Amax <- sim_pop_harv_output$parameters$Amax
    
```

## *`r full_name`* / `r short_name`


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 6.5, fig.width = 6.5}
plot_pop_vb_parms(sim_pop_harv_output)
```

Figure. Simulated population von Bertalanffy growth parameters for `r short_name`. Natural mortality is dependent on length via Lorenzen, overall **M = `r this_M`**. Max age is **`r this_Amax` years**. Vertical line is the population median for each parameter. The value of the correlation coefficient is printed on the lower right plot where the theoretical relationship between Linf and k is denoted by the broken red line.


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 5}
plot_pop_n_at_age(sim_pop_harv_output)
```

Figure. Simulated `r short_name` unfished population length composition.

|
|


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 4, fig.width = 5}
plot_fit_pop(sim_pop_harv_output)
```

Figure. Simulated `r short_name` unfished population with the fitted von Bertalanffy growth function.



``` {r PRFL, include = FALSE, eval = TRUE}

  short_name <- 'PRFL'
  full_name <- 'P. flavipinnis'
  sim_pop_harv_output <- PRFL
  this_M <- sim_pop_harv_output$parameters$M
  this_Amax <- sim_pop_harv_output$parameters$Amax
    
```

## *`r full_name`* / `r short_name`


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 6.5, fig.width = 6.5}
plot_pop_vb_parms(sim_pop_harv_output)
```

Figure. Simulated population von Bertalanffy growth parameters for `r short_name`. Natural mortality is dependent on length via Lorenzen, overall **M = `r this_M`**. Max age is **`r this_Amax` years**. Vertical line is the population median for each parameter. The value of the correlation coefficient is printed on the lower right plot where the theoretical relationship between Linf and k is denoted by the broken red line.


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 5}
plot_pop_n_at_age(sim_pop_harv_output)
```

Figure. Simulated `r short_name` unfished population length composition.

|
|


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 4, fig.width = 5}
plot_fit_pop(sim_pop_harv_output)
```

Figure. Simulated `r short_name` unfished population with the fitted von Bertalanffy growth function.




``` {r PRZO, include = FALSE, eval = TRUE}

  short_name <- 'PRZO'
  full_name <- 'P. zonatus'
  sim_pop_harv_output <- PRZO
  this_M <- sim_pop_harv_output$parameters$M
  this_Amax <- sim_pop_harv_output$parameters$Amax
    
```

## *`r full_name`* / `r short_name`


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 6.5, fig.width = 6.5}
plot_pop_vb_parms(sim_pop_harv_output)
```

Figure. Simulated population von Bertalanffy growth parameters for `r short_name`. Natural mortality is dependent on length via Lorenzen, overall **M = `r this_M`**. Max age is **`r this_Amax` years**. Vertical line is the population median for each parameter. The value of the correlation coefficient is printed on the lower right plot where the theoretical relationship between Linf and k is denoted by the broken red line.


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 5}
plot_pop_n_at_age(sim_pop_harv_output)
```

Figure. Simulated `r short_name` unfished population length composition.

|
|


```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 4, fig.width = 5}
plot_fit_pop(sim_pop_harv_output)
```

Figure. Simulated `r short_name` unfished population with the fitted von Bertalanffy growth function.

