---
# title: 
output: 
  word_document:
    reference_docx: PIFSC_style_simple.docx
# date: 
---

``` {r read_in_data, include = FALSE, eval = TRUE}
# knitr::opts_chunk$set(cache = TRUE)
# knitr::opts_chunk$set(eval = FALSE)

if (!require("pacman")) install.packages("pacman")
    pacman::p_load(reshape, dplyr, ggplot2, magrittr, assertthat, gridExtra, readxl, this.path, kableExtra, flextable, gt, officer, grid)

# turn off scientific notation in console output
  options(scipen=999)

  this_dir <- this.path::here(.. = 0)
  
# load the workspace containing our simulated populations from create_simulated_pops.R
  load(paste0(this_dir, "/simulated_pops.RData"))

# load in the workspace containing our growth parm estimates based on the original (pre Sette05 cruise) sample distributions
#   this workspace was made in create_simulated_pops.R and only needs to be updated if we change the values in
# BMUS_LH_sim_pop_parmaters.xls or if the list of "unfished CNMI" samples that Eva originally gave me gets changed.
  load(paste0(this_dir, "/original_sample_fits_2July.RData"))

# read in the modified LH Sampling functions
  source(paste0(this_dir, "/modify_LH_sample_function.R"))
  
# load the plotting functions we will use
  source(paste0(this_dir, "/plotting_functions.R")) 
  
# read in the .csv file with the species and lengths that we have
 have_lengths <- read.csv(paste0(this_dir,"\\cnmi_unfished_samples_update.csv"),header=T)
#  have_lengths <- read.csv(paste0(this_dir,"\\cnmi_unfished_samples.csv"),header=T)
  have_lengths <- have_lengths[,c(2,5,10)]
  
  names(have_lengths)[] <- c('species','length','type')
```

``` {r , include = FALSE, eval = TRUE}
# define leading values for this species
  short_name <- 'APRU'
  full_name <- 'Aphareus rutilans'
  sim_output <- sim_pop_harv_output <- APRU
  bin_width <- 5
  sim_fit_original <- APRU_sim_fit_org
    
# filter lengths    
  have <- subset(have_lengths, species ==  full_name)
  
# return the plan for the updated samples  
  sample_plan <- plan_updated <- get_plan(have, bin_width, original=FALSE)

# bootstrap samples and fit von B parms
  n_boots <- 100
  age_max <- sim_output$parameters$age_max
  save_bootstraps <- FALSE

  sim_fit_update <- fit_plan(sample_plan, sim_output, n_boots, age_max, save_bootstraps)
  
```

## *`r full_name`* / `r short_name`

```{r fig.cap = "", echo=FALSE,eval=TRUE,messages=FALSE,warning=FALSE, fig.height = 3, fig.width = 6.5}
plot_LH_have(have, bin_width)
```

```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 6.5}
parm_plots <- parm_abs_error_plot(sim_fit_original, sim_fit_update)
grid.arrange(grobs=parm_plots, ncol=3)
```

Figure. Samples of `r short_name` by length and simulated estimates of von Bertalanffy growth parameters based on samples available before the Sette 04 cruise (blue) and updated to include fish lengths observed during the cruise (green). The true population value for each parameter is shown as a broken black line.




``` {r , include = FALSE, eval = TRUE}
# define leading values for this species
  short_name <- 'ETCA'
  full_name <- 'Etelis carbunculus'
  sim_output <- sim_pop_harv_output <- ETCA
  bin_width <- 5
  sim_fit_original <- ETCA_sim_fit_org
    
# filter lengths    
  have <- subset(have_lengths, species ==  full_name)
  
# return the plan for the updated samples  
  sample_plan <- plan_updated <- get_plan(have, bin_width, original=FALSE)

# bootstrap samples and fit von B parms
  n_boots <- 100
  age_max <- sim_output$parameters$age_max
  save_bootstraps <- FALSE

  sim_fit_update <- fit_plan(sample_plan, sim_output, n_boots, age_max, save_bootstraps)
  
```

## *`r full_name`* / `r short_name`

```{r fig.cap = "", echo=FALSE,eval=TRUE,messages=FALSE,warning=FALSE, fig.height = 3, fig.width = 6.5}
plot_LH_have(have, bin_width)
```

```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 6.5}
parm_plots <- parm_abs_error_plot(sim_fit_original, sim_fit_update)
grid.arrange(grobs=parm_plots, ncol=3)
```

Figure. Samples of `r short_name` by length and simulated estimates of von Bertalanffy growth parameters based on samples available before the Sette 04 cruise (blue) and updated to include fish lengths observed during the cruise (green). The true population value for each parameter is shown as a broken black line.





``` {r , include = FALSE, eval = TRUE}
# define leading values for this species
  short_name <- 'ETCO'
  full_name <- 'Etelis coruscans'
  sim_output <- sim_pop_harv_output <- ETCO
  bin_width <- 5
  sim_fit_original <- ETCO_sim_fit_org
    
# filter lengths    
  have <- subset(have_lengths, species ==  full_name)
  
# return the plan for the updated samples  
  sample_plan <- plan_updated <- get_plan(have, bin_width, original=FALSE)

# bootstrap samples and fit von B parms
  n_boots <- 100
  age_max <- sim_output$parameters$age_max
  save_bootstraps <- FALSE

  sim_fit_update <- fit_plan(sample_plan, sim_output, n_boots, age_max, save_bootstraps)
  
```

## *`r full_name`* / `r short_name`

```{r fig.cap = "", echo=FALSE,eval=TRUE,messages=FALSE,warning=FALSE, fig.height = 3, fig.width = 6.5}
plot_LH_have(have, bin_width)
```

```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 6.5}
parm_plots <- parm_abs_error_plot(sim_fit_original, sim_fit_update)
grid.arrange(grobs=parm_plots, ncol=3)
```

Figure. Samples of `r short_name` by length and simulated estimates of von Bertalanffy growth parameters based on samples available before the Sette 04 cruise (blue) and updated to include fish lengths observed during the cruise (green). The true population value for each parameter is shown as a broken black line.




``` {r , include = FALSE, eval = TRUE}
# define leading values for this species
  short_name <- 'PRAU'
  full_name <- 'Pristipomoides auricilla'
  sim_output <- sim_pop_harv_output <- PRAU
  bin_width <- 2
  sim_fit_original <- PRAU_sim_fit_org
    
# filter lengths    
  have <- subset(have_lengths, species ==  full_name)
  
# return the plan for the updated samples  
  sample_plan <- plan_updated <- get_plan(have, bin_width, original=FALSE)

# bootstrap samples and fit von B parms
  n_boots <- 100
  age_max <- sim_output$parameters$age_max
  save_bootstraps <- FALSE

  sim_fit_update <- fit_plan(sample_plan, sim_output, n_boots, age_max, save_bootstraps)
  
```

## *`r full_name`* / `r short_name`

```{r fig.cap = "", echo=FALSE,eval=TRUE,messages=FALSE,warning=FALSE, fig.height = 3, fig.width = 6.5}
plot_LH_have(have, bin_width)
```

```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 6.5}
parm_plots <- parm_abs_error_plot(sim_fit_original, sim_fit_update)
grid.arrange(grobs=parm_plots, ncol=3)
```

Figure. Samples of `r short_name` by length and simulated estimates of von Bertalanffy growth parameters based on samples available before the Sette 04 cruise (blue) and updated to include fish lengths observed during the cruise (green). The true population value for each parameter is shown as a broken black line.



``` {r , include = FALSE, eval = TRUE}
# define leading values for this species
  short_name <- 'PRFI'
  full_name <- 'Pristipomoides filamentosus'
  sim_output <- sim_pop_harv_output <- PRFI
  bin_width <- 2
  sim_fit_original <- PRFI_sim_fit_org
    
# filter lengths    
  have <- subset(have_lengths, species ==  full_name)
  
# return the plan for the updated samples  
  sample_plan <- plan_updated <- get_plan(have, bin_width, original=FALSE)

# bootstrap samples and fit von B parms
  n_boots <- 100
  age_max <- sim_output$parameters$age_max
  save_bootstraps <- FALSE

  sim_fit_update <- fit_plan(sample_plan, sim_output, n_boots, age_max, save_bootstraps)
  
```

## *`r full_name`* / `r short_name`

```{r fig.cap = "", echo=FALSE,eval=TRUE,messages=FALSE,warning=FALSE, fig.height = 3, fig.width = 6.5}
plot_LH_have(have, bin_width)
```

```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 6.5}
parm_plots <- parm_abs_error_plot(sim_fit_original, sim_fit_update)
grid.arrange(grobs=parm_plots, ncol=3)
```

Figure. Samples of `r short_name` by length and simulated estimates of von Bertalanffy growth parameters based on samples available before the Sette 04 cruise (blue) and updated to include fish lengths observed during the cruise (green). The true population value for each parameter is shown as a broken black line.




``` {r , include = FALSE, eval = TRUE}
# define leading values for this species
  short_name <- 'PRFL'
  full_name <- 'Pristipomoides flavipinnis'
  sim_output <- sim_pop_harv_output <- PRFL
  bin_width <- 2
  sim_fit_original <- PRFL_sim_fit_org
    
# filter lengths    
  have <- subset(have_lengths, species ==  full_name)
  
# return the plan for the updated samples  
  sample_plan <- plan_updated <- get_plan(have, bin_width, original=FALSE)

# bootstrap samples and fit von B parms
  n_boots <- 100
  age_max <- sim_output$parameters$age_max
  save_bootstraps <- FALSE

  sim_fit_update <- fit_plan(sample_plan, sim_output, n_boots, age_max, save_bootstraps)
  
```

## *`r full_name`* / `r short_name`

```{r fig.cap = "", echo=FALSE,eval=TRUE,messages=FALSE,warning=FALSE, fig.height = 3, fig.width = 6.5}
plot_LH_have(have, bin_width)
```

```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 6.5}
parm_plots <- parm_abs_error_plot(sim_fit_original, sim_fit_update)
grid.arrange(grobs=parm_plots, ncol=3)
```

Figure. Samples of `r short_name` by length and simulated estimates of von Bertalanffy growth parameters based on samples available before the Sette 04 cruise (blue) and updated to include fish lengths observed during the cruise (green). The true population value for each parameter is shown as a broken black line.




``` {r , include = FALSE, eval = TRUE}
# define leading values for this species
  short_name <- 'PRZO'
  full_name <- 'Pristipomoides zonatus'
  sim_output <- sim_pop_harv_output <- PRZO
  bin_width <- 2
  sim_fit_original <- PRZO_sim_fit_org
    
# filter lengths    
  have <- subset(have_lengths, species ==  full_name)
  
# return the plan for the updated samples  
  sample_plan <- plan_updated <- get_plan(have, bin_width, original=FALSE)

# bootstrap samples and fit von B parms
  n_boots <- 100
  age_max <- sim_output$parameters$age_max
  save_bootstraps <- FALSE

  sim_fit_update <- fit_plan(sample_plan, sim_output, n_boots, age_max, save_bootstraps)
```

## *`r full_name`* / `r short_name`


```{r fig.cap = "", echo=FALSE,eval=TRUE,messages=FALSE,warning=FALSE, fig.height = 3, fig.width = 6.5}
plot_LH_have(have, bin_width)
```

```{r fig.cap = "", echo=FALSE, eval=TRUE, fig.height = 3, fig.width = 6.5}
parm_plots <- parm_abs_error_plot(sim_fit_original, sim_fit_update)
grid.arrange(grobs=parm_plots, ncol=3)
```

Figure. Samples of `r short_name` by length and simulated estimates of von Bertalanffy growth parameters based on samples available before the Sette 05 cruise (blue) and updated to include fish lengths observed during the cruise (green). The true population value for each parameter is shown as a broken black line.


